---
title: "Vignette for farspackage Coursera assignment"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fars_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(farspackage)
```

# Vignette for the farspackage

This package reads and summarises USA National Highway Traffic Safety Administration NHFTS [Fatality Analysis Reporting System FARS](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars) format data files.

## To load a FARS formatted data file

```{r}
fars_read("accident_2013.csv.bz2")
```

## To make a filename with a certain year as an input for other functions in this package

```{r}
make_filename(2020)
```

## To create a tibble from a FARS formatted data file(s) of a certain year

```{r}
fars_read_years(c(2013, 2014, 2015))
```

## To summarise the number of fatalities per month for a given year of a FARS formatted data file

```{r}
fars_summarize_years(c(2013, 2014, 2015))
```

## To produce a simple map of the location of fatalities within a certain state and year

```{r}
fars_map_state(6, 2013)
```

